A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-09-24 paper/ms.tex
update abstract

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.3\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler space telescope because it is nearby
  ($d=329\pm3\,{\rm pc}$) and it resembles the Sun.  Here we show
  using Gaia kinematics, TESS stellar rotation periods, and
  spectroscopic lithium abundances that Kepler\,1627 is a member of
  the \clusterage\ old $\delta$~Lyr cluster.  To our knowledge,
  Kepler\,1627Ab is the youngest planet with a precise age yet found
  by the main Kepler mission.  The Kepler data show two notable
  anomalies.  First, after removal of the stellar variability, the
  average Kepler transit profile appears to be asymmetric.  One
  possible explanation is that a dusty atmospheric outflow is present,
  but this remains to be confirmed.  Second, the individual transits
  show a correlation between the transit time and the local slope of
  the light curve.  Interpreted in a framework in which unresolved
  starspot-crossing events cause the transit timing variations, this
  suggests that the planet is on a prograde orbit.  We present
  Keck/HIRES observations that are consistent with the latter point, though
  the data do not have the precision necessary to claim a detection of the
  spectroscopic transit.  More broadly, the $\delta$~Lyr cluster
  is one of many stellar groups whose properties have been clarified
  using Gaia; many other exoplanet hosts belong to these new clusters.
  Verifying the results of Gaia clustering analyses using TESS
  rotation periods offers a promising path toward expanding the census
  of age-dated planets, and our corresponding understanding of
  planetary evolution.
\end{abstract}

>>>>

% 208 words (250 max)
\begin{abstract}
  % VERSION A
  Kepler\,1627A is a G8V star previously known to host a
  $3.3\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler space telescope because it is nearby
  ($d=329\pm3\,{\rm pc}$) and it resembles the Sun.  Here we show
  using Gaia kinematics, TESS stellar rotation periods, and
  spectroscopic lithium abundances that Kepler\,1627 is a member of
  the \clusterage\ old $\delta$~Lyr cluster.  To our knowledge,
  Kepler\,1627Ab is the youngest planet with a precise age yet found
  by the main Kepler mission.  The Kepler data show two notable
  anomalies: the average Kepler transit profile appears to be
  asymmetric, and the individual transits show a correlation between
  the transit time and the local slope of the light curve.  The former
  might be explained by a dusty atmospheric outflow; the latter could
  be explained by unresolved starspot crossings of a planet on a
  prograde orbit.  Broadly speaking, the $\delta$~Lyr cluster is one
  of many stellar groups whose properties have been clarified using
  Gaia; many other exoplanet hosts belong to these new clusters.
  Verifying the results of Gaia clustering analyses using TESS
  rotation periods offers a promising path toward expanding the census
  of age-dated planets, and our corresponding understanding of
  planetary evolution.
  %
  % % VERSION B
  % Kepler\,1627A is a G8V star previously known to host a
  % $3.3\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  % observed by the Kepler space telescope because it is nearby
  % ($d=329\pm3\,{\rm pc}$) and it resembles the Sun.  Here we show
  % using Gaia kinematics, TESS stellar rotation periods, and
  % spectroscopic lithium abundances that Kepler\,1627 is a member of
  % the \clusterage\ old $\delta$~Lyr cluster.  To our knowledge,
  % Kepler\,1627Ab is the youngest planet with a precise age yet found
  % by the main Kepler mission.  The Kepler data show two notable
  % anomalies.  First, after removal of the stellar variability, the
  % average Kepler transit profile appears to be asymmetric.  One
  % possible explanation is that a dusty atmospheric outflow is present,
  % but this remains to be confirmed.  Second, the individual transits
  % show a correlation between the transit time and the local slope of
  % the light curve.  Interpreted in a framework in which unresolved
  % starspot-crossing events cause the transit timing variations, this
  % suggests that the planet is on a prograde orbit.  We present
  % Keck/HIRES observations that are consistent with the latter point, though
  % the data do not have the precision necessary to claim a detection of the
  % spectroscopic transit.  More broadly, the $\delta$~Lyr cluster
  % is one of many stellar groups whose properties have been clarified
  % using Gaia; many other exoplanet hosts belong to these new clusters.
  % Verifying the results of Gaia clustering analyses using TESS
  % rotation periods offers a promising path toward expanding the census
  % of age-dated planets, and our corresponding understanding of
  % planetary evolution.
\end{abstract}
